Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-06 paper/paper.tex
Graphery

% \usepackage{showframe}

@@

\cref{figure:unconnected-33}

\cref{figure:unconnected-plain}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-33}
    \caption{Clique versus constraint programming, 33\% labelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, an
    instance-by-instance comparison of the two approaches: the colour at a point indicates the
    number of instances with these runtimes.} \label{figure:unconnected-33}
\end{figure}

% \begin{figure}[p]
%     \centering
%     \input{gen-graph-unconnected-33-breakdown}
%     \caption{Clique versus constraint programming, 33\% labelled, broken down by family.}
%         \label{figure:unconnected-33-breakdown}
% \end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-plain}
    \caption{Clique versus constraint programming, undirected, unlabelled. On the top, the cumulative
    number of instances solved by each approach, in under a certain time. On the bottom, an
        instance-by-instance comparison of the two approaches: the colour at a point indicates the
    number of instances with these runtimes.} \label{figure:unconnected-plain}
\end{figure}

% \begin{figure}[p]
%     \centering
%     \input{gen-graph-unconnected-plain-breakdown}
%     \caption{Clique versus constraint programming, undirected, unlabelled, broken down by family.}
%         \label{figure:unconnected-plain-breakdown}
% \end{figure}

@@

\paragraph{Connected, Undirected, 33\% Labelled} \cref{figure:connected-undir33} Above two seconds,
    the clique approach dominates except for three instances, and there is only one instance which
    the constraint programming model can solve but the clique model cannot (?? is this an EHP and does parallel get rid
    of it?). The clique model is unable to solve only ??  instances within one hour, ?? all of which
    have 90 or 100 vertices.  On the other hand, for trivial instances, the clique approach is often
    expensive due to the association graph construction.

\paragraph{Connected, Undirected, Unlabelled} \cref{figure:connected-plain}, looks like the clique
approach doesn't do so well\ldots

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-undir33}
    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, up to 100 vertices. On the top,
        the cumulative number of instances solved by each approach, in under a certain time. On the
        bottom, the association graph approach compared to the constraint programming approach with
        both branching and filtering.} \label{figure:connected-undir33}
\end{figure}

% \begin{figure}[p]
%     \centering
%     \input{gen-graph-connected-undir33-breakdown}
%     \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, broken down by family.}
%         \label{figure:connected-undir33-breakdown}
% \end{figure}

\begin{figure}[tb]
    \centering
    \input{gen-graph-connected-cp-undir33.tex}
    \caption{A pairwise comparison of different CP techniques for the connected, undirected, 33\%
        labelled variant with graphs of up to 80 vertices. The colour at a point indicates the
        number of instances with these runtimes, with darker colours representing more instances.}
        \label{figure:connected-cp-undir33}
\end{figure}

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain}
    \caption{Clique versus constraint programming, connected, undirected, unlabelled, up to 35 vertices. On the top, the
        cumulative number of instances solved by each approach, in under a certain time. On the
        bottom, the association graph approach compared to the constraint programming approach
    with both branching and filtering.}
\label{figure:connected-plain}
\end{figure}

% \begin{figure}[p]
%     \centering
%     \input{gen-graph-connected-plain-breakdown}
%     \caption{Clique versus constraint programming, connected, undirected, unlabelled, broken down by family.}
%         \label{figure:connected-plain-breakdown}
% \end{figure}

\begin{figure}[tb]
    \centering
    \input{gen-graph-connected-cp-plain.tex}
    \caption{Different CP techniques, connected, undirected, unlabelled, up to 35 vertices.}
        \label{figure:connected-cp-plain}
\end{figure}

>>>>

\usepackage{showframe}

@@

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-cumulative}
    \vspace*{1em}

    \centering
    \input{gen-graph-unconnected-heatmap}
    \caption{The cumulative number of instances solved in under a certain time: on the top, 33\%
        labelled graphs with up to 100 vertices, and in the middle, unlabelled and undirected graphs
        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the two
        approaches, with 33\% labelled graphs on the left, and unlabelled and undirected graphs on
        the right.} \label{figure:unconnected-cumulative}
\end{figure}

@@

\paragraph{Connected, Undirected, 33\% Labelled}

\paragraph{Connected, Undirected, Unlabelled}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-cumulative}
    \vspace*{1em}

    \centering
    \input{gen-graph-connected-heatmap}
    \caption{The cumulative number of connected instances solved in under a certain time: on the
        top, 33\% undirected labelled graphs with up to 100 vertices, and in the middle, unlabelled
        and undirected graphs with up to 35 vertices. On the bottom row, an instance-by-instance
        comparison of the association and MAC both approaches, with 33\% labelled graphs on the
        left, and unlabelled and undirected graphs on the right.} \label{figure:connected-cumulative}
\end{figure}

\begin{figure}[tb]
    \centering
    \input{gen-graph-connected-cp.tex}
    \caption{A pairwise comparison of different CP techniques. The colour at a point indicates the
    number of instances with these runtimes, with darker colours representing more instances.}
        \label{figure:connected-cp}
\end{figure}
